---
title: 'Peer-graded Assignment:'
author: "A Johnson"
date: "September 20, 2019"
output:
  slidy_presentation: default
  ioslides_presentation: default
subtitle: R Markdown Presentation & Plotly
---

## Background

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity! 

The rubric contains the following two questions:

        - Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?

        - Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?

## Data Source

I pulled name and address information from Google as of 9/17/19 by searching "Oklahoma City" + "dispensary". Given this info, I mapped the addresses of dispensaries using the latitude and longitude of each address (see below for map). Dispensaries were color-coded based on the type of naming convention used: whether the business name included the word "dispensary", whether the business name included "wellness" or "medical", and all other businesses. 

```{r, include = FALSE}
#setwd("C:/Users/ajohns34/Box/Data Science Specialization/Assignment 14")

#Read in the data:
    disp = read.csv("./Dispensaries in OKC.csv", header = T)
    library(plotly)
```

## Plotly Code

Code used to generate the plot. The plot appears on the next slide.
```{r plotcode, tidy=TRUE}
f = list(family = "Courier New, monospace", size = 18, color = "#7f7f7f")
x = list(title = "Latitude", titlefont = f)
y = list(title = "Longitude", titlefont = f)
p = plot_ly(x = disp$Lat, y = disp$Long, type = "scatter", mode = "markers", color = disp$Type) %>%
    layout(xaxis = x, yaxis = y)

```

## Latitude and Longitude of Dispensaries in Oklahoma City, OK

```{r map, echo = FALSE}

    p    
    
```


